---
title: "R Notebook"
output: html_notebook
---

```{r}
library(RPostgreSQL)
library(DBI)
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)
db_connect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "omni_employees.sql", host = "localhost")
rm(postgresql_username, postgresql_password)


```
```{sql connection=db_connect}
SELECT * 
FROM employees



```

```{sql connection=db_connect}
SELECT *
FROM pay_details
```




```{r}


```

All employees who work in Human Resources

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE department = 'Human Resources'
```

First Name, Last Name and Country of everyone in Legal


```{sql connection=db_connect}
SELECT 
country,
department,
first_name,
last_name
FROM employees
WHERE department = 'Legal'

```
Count the number of employees based in Portugal. (i think there might be a better way to do this)

```{sql connection=db_connect}
SELECT 
  COUNT(*) AS portugal
FROM employees
WHERE country = 'Portugal'
```
employees from Portugal or Spain

```{sql connection=db_connect}
SELECT 
  COUNT(*) AS portugal_or_spain
FROM employees
WHERE country = 'Portugal' OR country = 'Spain'
```

pay detials lacking an account number


```{sql connection=db_connect}
select *
FROM pay_details
WHERE local_account_no IS NULL

```
Are there any pay_details record lacking both a local_account_no and iban number?

I think there's a better way to do this one too.

```{sql connection=db_connect}
select *
FROM pay_details
WHERE local_account_no IS NULL AND iban IS NULL


```
Get a list of employees first names and last names ordered alphabetically by their last name (put any nulls last).

```{sql connection=db_connect}
SELECT *
FROM employees
ORDER BY last_name ASC NULLS LAST
LIMIT 1000
```

Get a list of employees first names and last names ordered alphabetically by their last name (put any nulls last).  Chopped by a comma!!!

```{sql connection=db_connect}
SELECT 
first_name,
last_name
FROM employees
ORDER BY last_name ASC NULLS LAST

```
Get a list of employees first names, last names and countries, ordered alphabetically first by their country and second by their last name (put any nulls last).


```{sql connection=db_connect}
SELECT 
first_name,
last_name,
country
FROM employees
ORDER BY country DESC, last_name
NULLS LAST
```

Find the top ten highest paid employees in the corporation.

```{sql connection=db_connect}
SELECT *
FROM employees
ORDER BY salary DESC
```
Find the first name, last name and salary of the lowest paid of the employees in Hungary

There's only one employee from Hungary....

```{sql connection=db_connect}
SELECT 
first_name,
last_name,
salary
FROM employees
WHERE country = 'Hungary'
ORDER BY salary ASC
Limit 5
```

How many employees have a first name beginning with ‘F’?

```{sql connection=db_connect}
SELECT * 
FROM employees
WHERE first_name Like 'F%'


```
Find all the details of any employees with a ‘yahoo’ e-mail address?

```{sql connection=db_connect}
SELECT * 
FROM employees
WHERE email Like '%yahoo%'
```
Count the number of pension enrolled employees not based in either France or Germany.

I don't think i've got this one right. changing the AND to OR changes the number massively. 

```{sql connection=db_connect}
SELECT 
  COUNT(*) AS FG_Pension 
FROM employees
WHERE country != 'France' OR country != 'Germany'
AND pension_enrol = TRUE
```
Breakdown the numbers of employees enrolled, not enrolled and whose enrollment status is unknown in the corporation pension scheme.  I am bested by this one 

```{sql connection=db_connect}
SELECT 
  COUNT(*) AS FG_Pension 
FROM employees
WHERE pension_enrol = TRUE

```
What is the maximum salary among employees in the Engineering department who work 1.0 full-time equivalent hours?

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE department = 'Engineering' 
AND fte_hours = 1.0
ORDER BY salary DESC
Limit 1
```


Obtain a count by department of the employees who started work with the corporation in 2003.

```{sql connection=db_connect}
SELECT*
FROM employees
WHERE start_date BETWEEN '2003-01-01' AND '2003-12-31'
ORDER BY department
```


Obtain a count by department of the employees who started work with the corporation in 2003.

```{sql connection=db_connect}
SELECT
department, 
COUNT(department) AS 2003_employee
FROM employees
WHERE WHERE start_date BETWEEN '2003-01-01' AND '2003-12-31'
GROUP BY department
```

```{r}

```

