---
title: "R Notebook"
output: html_notebook
---
```{r}

```

```{r}
library(RPostgreSQL)
library(DBI)
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)

db_connect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "acme_employees", host = "localhost")

rm(postgresql_username, postgresql_password)
```


```{r}
dbListTables(db_connect)
```
I am running this to get an idea of what info is contained on each table. 
```{sql connection=db_connect}
SELECT * FROM 
employees


```


```{sql connection=db_connect}
SELECT * FROM
teams
```
```{sql connection=db_connect}
SELECT * FROM
feedbacks
```
Create a new data.frame containing the details of all employees held in the database


```{sql connection=db_connect}

```
This code lists all the tables in the database to which you are connected, it runs in R. 

```{r}
dbListTables(conn = db_connect)
```

```{r}
dbListFields(conn = db_connect, name = "employees")
```

```{r}
dbListFields(conn = db_connect, name = "feedbacks")
```

Create a new data.frame containing the details of all employees held in the database

```{r}
employee_data <- dbGetQuery(conn = db_connect, statement = "SELECT * FROM employees")
employee_data
```
```{sql connection=db_connect}
employees

```
```{r}
employee_data
```

```{sql connection=db_connect}

```
Retrieve the records for all employees again, but this time add a field full_name containing the first_name and last_name of each employee separated by a space.


```{r}
employee_data["full_name"] <- c("first_name", "last_name")
employee_data
```
Retrieve the records for all employees again, but this time add a field full_name containing the first_name and last_name of each employee separated by a space.


```{r}
employee_data$full_name = paste(employee_data$first_name,employee_data$last_name)
employee_data
```
Retrieve the details of all employees again, but this time listing their team name (as team_name), rather than their team_id.

This is frustrating as i think the way to solve it is by changing the integer to a character but i cant figure out how to do it, have tried numerous ways and googled error messages, went through notes and prev code but can't figure it out. 
```{sql connection=db_connect}
SELECT 
  a.*, 
  d.*
FROM employees AS a 
LEFT JOIN teams AS d
ON a.team_id AS d.name
```

Bit Harder] Do a breakdown of the number of employees per team (here we want two columns: team_name and num_employees). Order the table in decreasing number of employees. Include all teams, even if they have no employees.


```{sql connection=db_connect}
SELECT *
FROM 


```





```{r}

```

