---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

#Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
nrow(backpack)
ncol(backpack)
backpack
```

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  scale_y_continuous(breaks = seq(12)) +
  scale_x_continuous(breaks = seq(35)) +
  ylab("number of students") +
  xlab("backpack weight") +
geom_histogram(binwidth = .5, colour = "dark blue", fill = "black") 
```

#now i'm looking into the differences in backpack weight between males and females. 

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  scale_y_continuous(breaks = seq(12)) +
  scale_x_continuous(breaks = seq(35)) +
  ylab("number of students") +
  xlab("backpack weight") +
  facet_grid( ~ sex) +
geom_histogram(binwidth = .5, colour = "dark blue", fill = "black")
```

# looking at the relationship between bodyweight and backpack weight now.  


```{r}
ggplot(backpack) +
  aes(x = body_weight) +
  geom_histogram(col = "white") +

  facet_wrap( ~backpack_weight, nrow = 4
              )
```

```{r}
backpack %>%
  select(back_problems) %>%
  

  
```
Question 6.

What proportion of students report back pain?  32%

```{r}
backpack %>% count(back_problems)
```

Question 7.

Is this proportion different between men and women?

```{r}
ggplot(backpack,aes(x = back_problems, fill = sex)) + 
    geom_bar(position = "fill")
```

