---
title: "R Notebook"
output: html_notebook
---

#2.2.1
Write a function which multiples all numbers by 15 and adds 4.

```{r}
library(dplyr)
```

```{r}
x <- 2
multiply_by_15_adds_4 <- function(x){
  y <- x * 15
return(y + 4)
}

```

```{r}
multiply_by_15_adds_4 (1)
multiply_by_15_adds_4 (2)
multiply_by_15_adds_4 (3)
```

#  2.2.2
Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.

#i know this isn't right but i can't get it to run on more than one thing at a time, i also know i've not created a function out of it. I could create two more lines of code for checking for "duck" & "pigeon" but i know that's not right too. How can i add in extra elemnts to an ifelse function?? I know i should look something like


bird_function <- function {ifelse(bird_list == "goose" or "duck" or "pigeon, "bird", "notbird")}  

But can't get it to work. 


```{r}

bird_function <- function (bird_function) {ifelse(bird_list == "goose", "bird", "notbird")}
 bird_function()
```


#2.2.3
Write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”.

Same as the one above, i can't seem get more than one function working, i'm just getting errors every 
```{r}
multiply_by_10 <- function(x){
  return(x*10)
  ifelse(numeric(return(x)), FALSE, "invalid input")}

multiply_by_10(2)
multiply_by_10(5.3)

multiply_by_10(7)
```


2.3 ifelse(), recode() and case_when()
For these questions, we want you to code solutions without using if statements or loops.

Each question can be answered with either ifelse(), recode() or case_when(). Decide which function you think works best and use it to answer the question.

Remember to load dplyr to use recode() and case_when().
2.3.1
For the vector below, make a new vector which is equal to “Big” every time the element of sizes is greater than 10, and equal to “Small” every time the element of sizes is less than or equal to 10.
```{r}
sizes <- c(13, 15, 10, 8, 22)
big_vector <- c(  ifelse(sizes <= 10, "small", "big"))
big_vector
```
2.3.2
For the vector below convert:

apple → alpaca

banana → bonobo

cherry → chipmunk
```{r}
fruit <- c("apple", "apple", "banana", "cherry", "cherry")

fruit_vector <- gsub("apple", "alpaca", fruit)


```
Couldn't figure out how to get multiple arguments into the function. Also i\ve gone back in and changed one of these, hence the wonkyness of it.  Went back through notes and think bottom version is closer to the answer using x <- as.factor( c("apple", "apple", "banana", "cherry", "cherry"))
dplyr::recode(x , "apple" = "alpaca", "banana" = "bonobo", "cherry" = "chipmonk") 

```{r}
x_fruit <- gsub("apple", "alpaca", fruit) 
x_fruit1 <- gsub("banana", "bonobo", fruit)
x_fruit
```
```{r}
x <- as.factor( c("apple", "apple", "banana", "cherry", "cherry"))
dplyr::recode(x , "apple" = "alpaca", "banana" = "bonobo", "cherry" = "chipmonk")
```


2.3.3
The two vectors below show the ages at marriage of each member of a couple. The first elements of each vector correspond to the first couple, the second elements to the second couple, and so on.


Create a new vector which is equal to:

“Wife older” whenever the wife’s age is highest “Husband older” when the husband’s age is highest “Same age” when they are the same age

Prob didn't have to create a data frame but it was good practise. 

I could add in another 
```{r}
wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)
age_matrix <- matrix(wife_age, nrow =1, ncol =5)
age_matrix
```

```{r}
age_matrix <- matrix(wife_age, nrow = 1, ncol = 5)
age_matrix
```

```{r}
couples <- c("couple_1", "couple_2", "couple_3", "couple_4", "couple_5")
wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)
```

```{r}
data.frame(couples, wife_age, husband_age)
```

```{r}
married_frame <- data.frame(couples, wife_age, husband_age)
married_frame
```

```{r}
wifeolder <- subset(married_frame, wife_age >= husband_age)
print(wifeolder)

```

```{r}
husband_older <- subset(married_frame, husband_age >= wife_age)
print(husband_older)
```

```{r}
as.numeric(wife_age)
```

```{r}
married_frame$
```
This is the closest i can get...obv wrong as not returning "same age"
```{r}
x <- wife_age
y <- husband_age
married_frame$wife_age
case_when(
  x >= y ~ "wife older",
  y >= x ~ "husband older",
  x == y ~ "same age"

)
```

I look forward to seeing the answers to these...

```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
my_list
```

```{r}
for (character in my_list) {
  print(my_list)
}
  
  

```

