---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(outliers)
```
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.
```{r}
codeclan_tweets <- read_csv("4_homework/data/code_clan_tweets.csv")
```
```{r}
codeclan_tweets
```
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.
```{r}
dim(codeclan_tweets)
```
First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

average number of favourites for each tweet
```{r}
meantweets <- mean(codeclan_tweets$favorite_count) 
 
meantweets

```
The total amount of times codeclan tweets have been favourited. 
```{r}
meantweets <- sum(codeclan_tweets$favorite_count)
meantweets
```


```{r}
boxplot(codeclan_tweets$favorite_count)
```
```{r}

```



Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).


```{r}
total_favourites <- sum(codeclan_tweets$favorite_count)
total_favourites
```









