---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(janitor)
library(skimr)
install.packages("mass")
library(MASS)
```
Loading the data from the csv. 

```{r}
phone_data <- X20190928_items
clean_names(phone_data)
```
removing the columns i don't need. 
```{r}
phone_data <- 
  phone_data %>%
  select(-c(url, image, reviewUrl, prices, asin,))
```
taking out another column i don't need. 
```{r}
phone_data <- 
  phone_data %>%
  select(-c(title))
```

```{r}
glimpse(phone_data)
```
just checking for spelling and stuff in the brand column, seeing if any further cleaning required. 
```{r}
unique(phone_data$brand)
```
```{r}
phone_data
```
Find the brand with the highest numbers of phones in the dataset.

```{r}
str_count(phone_data, "Samsung")
```

```{r}
ggplot(phone_data) +
  aes(x = brand, y = rating, fill = brand) +
  geom_col()
```
Here i'm seeing what the mean and standard of the ratings for Samsung phones are. 
```{r}
review_stats <- phone_data %>%
  filter(brand == "Samsung") %>%
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
review_stats
```
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

Based on the visual info below, the data is normally distributed.

```{r}
phone_data %>% 
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", fill = "blue", bins = 25) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = 3.5733, 
      sd = 0.6847859
    ),
    col = "red"
  )
```
proportions of ratings within one-, two- and three standard deviations of the mean. 

within one sd of mean is 0.79

```{r}
samsung_ratings <- phone_data %>% 
  filter(brand == "Samsung") 
samsung_ratings

samsung_ratings %>%
  filter(rating >= 3.5733 - 0.6847859) %>%
  filter(rating <= 3.5733 + 0.6847859) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```


within 2 of sd
```{r}
samsung_ratings %>%
  filter(rating >= 3.5733 - 2*0.6847859) %>%
  filter(rating <= 3.5733 + 2*0.6847859) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```
within 3
```{r}
samsung_ratings %>%
  filter(rating >= 3.5733 - 3*0.6847859) %>%
  filter(rating <= 3.5733 + 3*0.6847859) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```

