---
title: "R Notebook"
output: html_notebook
---
sampling distribution
inferential statistics
bias and sampling
bootstrapping and confidence intervals

```{r}
library(tidyverse)
library(janitor)
install.packages("infer")
library(infer)
```

```{r}
read_csv("data/ames.csv")
```

```{r}
ames <- clean_names(ames)
```

Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
lot_summary <- ames %>%
  summarise(
    lot_area_mean = mean(lot_area)
    
  )

lot_summary
```
Looks to me like it is not normally distributed. It is right skewed and has extreme outliers (large farms?) 


```{r}
ames %>%
  ggplot(aes(x = lot_area)) +
  geom_histogram(col = "black", bins = 1000) 
```
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

First i'm using infer to specify, generate and calculate. then using ggplot to visualise below. 

```{r}
lot_mean <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")


  mean(lot_mean$stat)
```
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
lot_mean %>%
  ggplot(aes(x = stat)) +
  geom_histogram(col = "black", fill = "blue", bins = 100)+
```
Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
lot_ci <- lot_mean %>%
  get_confidence_interval(level = 0.95, type = "percentile")

lot_ci

```

```{r}
lot_mean %>%
  visualise(bins = 100) +
  shade_confidence_interval(endpoints = lot_ci)
```
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?


```{r}
lot_ci_99 <- lot_mean %>%
  get_confidence_interval(level = 0.99, type = "percentile")

lot_ci_99
```
Is it narrower or broader than the 95% CI? Does that make sense?

Yes , higher the CI, the bigger the difference bettwen the upper and lower number as they've got less to fit in on either side.

```{r}
lot_ci$upper_ci -lot_ci$lower_ci
lot_ci_99$upper_ci - lot_ci_99$lower_ci
```

Calculate the point estimate of the mean(lot_area)  ??!??!?!
10150.27
```{r}
ames_before_1920 <-
  
  ames %>%
  mutate(before_1920 = as.numeric(year_built < 1920))


```





```{r}
bootstrap_distn_200 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 200, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_1000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_10000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_30000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 30000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_50000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 50000, type = "bootstrap") %>%
  calculate(stat = "mean")
```

```{r}
bootstrap_distn_1000
bootstrap_distn_10000
bootstrap_distn_30000
bootstrap_distn_50000
```

