---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(broom)
library(animation)
```

```{r}
computers

```

```{r}
computers %>%
  ggplot(aes(x = hd, y = ram)) +
  geom_point()
```
in answer to the suitability to cluster.... I dunno, kinda.....Logic is telling me yes otherwise what's the point in the hiomework but looking at the data it looks a bit organised and non linear.  So....who knows?? Yes i suppose it is, there's visually soe grouping on the y axis (RAM) around like 4, 8, 16 (GB?) with a wider spread on the x axis.

```{r}
computers_clean <- computers %>%
  select(c(ram, hd))

computers_clean
```
```{r}
summary(computers_clean)
```


First i'm gonna scale the data.   

```{r}
computers_scale <- computers_clean %>%
  mutate_all(scale)
```

```{r}
computers_scale
```

```{r}
clustered_computers <- kmeans(computers_scale, centers =  4, nstart = 25)

clustered_computers
```
Next i'm going to use 

Tidy

Glance 

Augments

to have a look at the clusters and the data contained within in a bit more detail. 

Here i'm looking at info about the mean and the size of each cluster. 
```{r}
tidy(clustered_computers, 
     col.names = colnames(computers_scale))
```
Now i'm looking at info about the full clustering. 

```{r}
glance(clustered_computers)
```
This function shows me which cluster each data point has been added to.  (comparing the new data i've clustered with the old data. )
```{r}
augment(clustered_computers, computers)
```

```{r}
computers_scale %>%
  kmeans.ani(centers = 4)
```
Now i'm going to look at how many clusters i need in order to have the max heterogenity. 

```{r}
max_k <- 20

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(computers_scale, .x, nstart = 25)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, computers)
  )

k_clusters

```
unpacking the tibble to have a look at the tot.withinss which is my key variable. 
```{r}
comp_clusterings <- k_clusters %>%
  unnest(glanced)

comp_clusterings
```

```{r}
ggplot(comp_clusterings, aes(x=k, y=tot.withinss)) +
  geom_point() +
    geom_line() +
    scale_x_continuous(breaks = seq(1, 20, by = 1))
```

as i predicted....4. so the plot. below is as good as it gets. 

```{r}
computers_scale %>%
  kmeans.ani(centers = 4)
```

```{r}
comp_clusterings %>% 
  unnest(cols = c(augmented)) %>%
  filter(k <= 4) %>%
 ggplot(aes(x = ram, y = hd)) +
  geom_point(aes(color = .cluster)) + 
  facet_wrap(~ k)
```

still unsure if clustering was suitable given the weird distribution.  k = 3 might have been an option too. 