---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(infer)
install.packages("arules")
install.packages("arulesViz")
library(arules)
library(arulesViz)
library(CodeClanData)
```
83 rows 11 cols
```{r}
msleep

```
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies. 

Jabberwockies = 7 hours
sampeled population of animals = 10.433 hours. 

```{r}

msleep_mean <- 
  mean(msleep$sleep_total)

msleep_mean
```
Now i need to test if that 3.43 hours difference is statistically significant. Start with having a look at the data

```{r}
msleep %>%
  select(sleep_total) %>%
  ggplot(aes(x = sleep_total)) +
  geom_histogram(col = "black", fill = "blue", bins = 40)
```
This chunk gives me the null distribution of the data given. 
```{r}
null_distribution <- msleep%>%
specify(response = sleep_total) %>%
  hypothesise(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

null_distribution
```
This is me looking at the confidence intervals at 95% so 95% of the means when sampled using bootstrap as above fall between this range. which means that our jabberwockie at 7 hours falls far outwith that mean.  

```{r}
lot_area_ci95 <- null_distribution %>%
  get_ci(level = 0.99, type = "percentile")
lot_area_ci95
```
Yeah so 99% of the time the mean of the sleep total lies between 9.2 & 


```{r}
null_distribution %>%
  visualise(bins = 30) +
  shade_ci(endpoints = lot_area_ci95)
```

```{r}
null_distribution %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_rating, direction = "less")
```




```{r}
omni_sleep <- msleep %>%
  filter(vore == "omni")  %>%
  summarise(mean_sleep_omni = mean(sleep_total))
omni_sleep
  
```

```{r}
herb_sleep <- msleep %>%
  filter(vore == "herbi")  %>%
  summarise(mean_sleep_herb = mean(sleep_total))
herb_sleep
```

